Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-03 p2/p2.Rmd
.

```{r, fig.cap="Type II errors for different levels of coarseness of profiles."}
e1<-errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + xlab("Profile Coarseness")+
  ylab("Type II error")

@@

total1<- errors_sig_c %>% ggplot(aes(x = coarse, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line()  + geom_point(data= errors2 %>% filter(wv==30), aes(shape="profiles")) + geom_line(data=errors2 %>% filter(wv==30), aes(shape="profiles")) + theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + ylab("Total error")

@@

```{r prof_missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests by the window optimization size, wo, and ground truth. Test results from different sources have a much higher chance to fail, raising the question, whether failed tests should be treated as rejections of the null hypothesis of same source."}
nsp <- allp %>% group_by(wv, wo, match, coarse) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value)),
  missperc = miss/85491*100
)

@@

#ns1<- ns[which(ns$wv == c(30,50), arr.ind = T),]
miss_1<- nsp %>% filter(wv == 30) %>%
#ns %>% filter(wv == c(30, 50)) %>%
  ggplot(aes(x = coarse, y = missperc, shape= "profile", colour = factor(match))) + 
  #geom_smooth(method="auto", size=.5, se=FALSE) +
  geom_point(size = 2) + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("Coarseness") +
  scale_colour_brewer("Match", palette="Set1") + geom_point(data=ns  %>% filter(wv %in% c(30,50)) , aes(shape="signature"), size = 2)# + scale_colour_brewer("Match", palette="Set2") #+geom_smooth(method="auto", size=.5, se=FALSE) 
  #scale_shape_discrete("Size of \nvalidation\nwindow, #wv")

>>>>

```{r, fig.cap="Type II errors for different levels of coarseness."}
e1<-errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + xlab("Profile Coarseness")+
  ylab("Type II error")

@@

total1<- errors_sig_c %>% ggplot(aes(x = coarse, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line()  + geom_point(data= errors2 %>% filter(wv==30), aes(shape="profiles")) + geom_line(data=errors2 %>% filter(wv==30), aes(shape="profiles")) + theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + xlab("Coarseness") +ylab("Total error")

@@

```{r prof_missings, fig.width=8, fig.height=5, fig.cap="Bottom row shows Total error and Number of failed tests by the window validation size, wv, and ground truth, while the top row shows Total error and Number of failed tests with Coarseness for both profiles and signatures"}
nsp <- allp %>% group_by(wv, wo, match, coarse) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value)),
  missperc = miss/85491*100
)

@@

#ns1<- ns[which(ns$wv == c(30,50), arr.ind = T),]
miss_1<- nsp %>% filter(wv == 30) %>%
#ns %>% filter(wv == c(30, 50)) %>%
  ggplot(aes(x = coarse, y = missperc, shape= "profile", colour = factor(match))) + 
  #geom_smooth(method="auto", size=.5, se=FALSE) +
  geom_point(size = 2) + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("Coarseness") +
  scale_colour_brewer("Match", palette="Set1") + geom_point(data=ns_sig_c  %>% filter(wv %in% c(30,50)) , aes(shape="signature"), size = 2)# + scale_colour_brewer("Match", palette="Set2") #+geom_smooth(method="auto", size=.5, se=FALSE) 
  #scale_shape_discrete("Size of \nvalidation\nwindow, #wv")
